Genetic Algorithm Based Formula Generation for Curve Fitting in Time Series Forecasting Implemented as Mobile Distributed Computing

### 2019-05-15 Genetic-Algorithm-Based-Formula-Generation-for-Curve-Fitting-in-Time-Series-Forecasting-Implemented-as-Mobile-Distributed-Computing/paper.tex
Some more text was added.

\usepackage{mathptmx}
\usepackage{helvet}
\usepackage{courier}
\usepackage{type1cm}
\usepackage{makeidx}
\usepackage{graphicx}
\usepackage{multicol}
\usepackage[bottom]{footmisc}
\usepackage{listings}
\usepackage{xcolor}
\definecolor{very-light-gray}{gray}{0.95}

@@

There are different ways in which arithmetic expressions can be presented into the computer memory. One of the most used representations is an expression tree. Such representation is convenient in many cases, but for the current research arithmetic expressions are encoded as simple text strings.

\begin{lstlisting}[caption={Genetic algorithm pseudo-code.},label={lst01},backgroundcolor=\color{very-light-gray},frame={single}]
begin
  t = 0;
  initialize P(t);
  evaluate structures in P(t);
  while termination condition not satisfied do
  begin
    t = t + 1;
    select_repro C(t) from P(t-1);
    recombine and mutate structures in C(t)
    forming C’(t);
    evaluate structures in C’(t);
    select_replace P(t) from C’(t) and P(t-1);
  end
end
\end{lstlisting}

@@

\begin{figure}[b]
\sidecaption
\includegraphics[scale=0.12]{fig01.png}
\caption{EUR/USD rate for two months.}
\label{fig01}
\end{figure}

Publicly available data are used for EUR/USD rate for two months in 2019 year (Fig. \ref{fig01}). Bars in the chart shows the real world price. The line above the bars is the line of the formula generated by the proposed genetic algorithm.

\begin{table}
\caption{Genetic algorithm parameters.}
\label{tab01}
\begin{tabular}{p{6.9cm}p{4.4cm}}
\hline\noalign{\smallskip}
\textbf{Parameter} & \textbf{Value} \\
\noalign{\smallskip}\svhline\noalign{\smallskip}
generation gap & 0.97 \\
crossover rate & 0.95 \\
mutation rate & 0.03 \\
maximum generations & 100 \\
number of individuals & 37 \\
number of variables & floating \\
inserted rate & 100 \% \\
\noalign{\smallskip}\hline\noalign{\smallskip}
\end{tabular}
\end{table}

@@

@@

>>>>

\usepackage{mathptmx}
\usepackage{helvet}
\usepackage{courier}
\usepackage{type1cm}
\usepackage{makeidx}
\usepackage{graphicx}
\usepackage{multicol}
\usepackage[bottom]{footmisc}
\usepackage{placeins}
\usepackage{listings}
\usepackage{xcolor}
\definecolor{very-light-gray}{gray}{0.95}

@@

There are different ways in which arithmetic expressions can be presented into the computer memory. One of the most used representations is an expression tree. Such representation is convenient in many cases, but for the current research arithmetic expressions are encoded as simple text strings. The crossover operator in this case is simple single cut and swap. Mutation is organized as random change of a mathematical operator, random change of a mathematical function and random change of a operand.

\begin{lstlisting}[caption={Genetic algorithm pseudo-code.},label={lst01},backgroundcolor=\color{very-light-gray},frame={single}]
begin
  t = 0;
  initialize P(t);
  evaluate structures in P(t);
  while termination condition not satisfied do
  begin
    t = t + 1;
    select_repro C(t) from P(t-1);
    recombine and mutate structures in C(t)
    forming C’(t);
    evaluate structures in C’(t);
    select_replace P(t) from C’(t) and P(t-1);
  end
end
\end{lstlisting}
\FloatBarrier

For the genetic algorithm a classical implementation is proposed (Listing \ref{lst01}) as described in \cite{baeck01}.

@@

\begin{figure}[b]
\sidecaption
\includegraphics[scale=0.12]{fig01.png}
\caption{EUR/USD rate for two months.}
\label{fig01}
\end{figure}
\FloatBarrier

Publicly available data are used for EUR/USD rate for two months in 2019 year (Fig. \ref{fig01}). Bars in the chart shows the real world price. The line above the bars is the line of the formula generated by the proposed genetic algorithm. The approximation of the price values follows the shape of the bars.

\begin{table}
\caption{Genetic algorithm parameters.}
\label{tab01}
\begin{tabular}{p{6.9cm}p{4.4cm}}
\hline\noalign{\smallskip}
\textbf{Parameter} & \textbf{Value} \\
\noalign{\smallskip}\svhline\noalign{\smallskip}
generation gap & 0.97 \\
crossover rate & 0.95 \\
mutation rate & 0.03 \\
maximum generations & 100 \\
number of individuals & 37 \\
number of variables & floating \\
inserted rate & 100 \% \\
\noalign{\smallskip}\hline\noalign{\smallskip}
\end{tabular}
\end{table}
\FloatBarrier

In 100 generations the genetic algorithm proposes a solution presented with the formula in Eq. \ref{equ01}.

@@

The equation has few terms with sine and logarithmic functions used. The input of the equation is time value (number of days). The output of the equation is a prediction of the EUR/USD rate.

@@

\bibitem{baeck01} Baeck, T., Fogel, DB., Michalewicz, Z., \textbf{\textit{Evolutionary Computation 1 - Basic Algorithms and Operators}}, Institute of Physics Publishing - Bristol and Philadelphia, p. 65--68, 2000.
